### 2009-10-20 latex/paper1/contents.tex

% TODO: this paragraph can mostly disappear.
%
The time spent on the maintenance of a software system can be affected by the
assignment of developers to implementation components of the system.
If two development teams are responsible for maintaining components that are
highly interdependent, they need to coordinate their work often in order avoid
code duplication and breaking each other's component funcionality.

Therefore, to optimize the development of a system, a manager can decompose the
system into modules, or groups of components, so that there are as few
inter-module dependencies as possible. % (i.e., the modules are weakly coupled).
%Each module is, then, threated as an unit of work assignment \cite{Parnas1972}:
Then, each module is assigned to one team and, because of the little inter-module
dependency, the communication between teams is reduced, therefore speeding up
the development.

%********** 
%
%Large software systems need to be decomposed in smaller parts in order to be
%effectively maintained by groups of developers working concurrently. If a system
%is poorly documented, 
%
%**********
%
%Even if a
%system is poorly documented, a software manager should be able to decompose it into 
%modules with few dependencies between them, so 
%
%find relatively
%independent modules in it, so each development team 
%
% A software
%manager should be
%**********
%
% The task of
%finding cohesive modules in the source code
%
%Although
%dependency analysis tools can aid in the task of 
%Dependency
%analysis

To decompose a system into modules, a manager needs to have global knowledge of
the dependencies between its components. Although dependency analysis tools can
extract such information from the source code of the system, the task of finding
a good decomposition can be overwhelming because of the large number of
components and dependencies that need to be considered.

Software clustering algorithms, also known as architecture recovery algorithms
\cite{Mancoridis1998,Anquetil1999,Tzerpos2000,Andritsos2005},
%\cite{Pollet2007}, 
automatically decompose a software system by analyzing the network of
dependencies between its components. %Although many algorithms have been
%proposed, few comparative studies exist.  empirical studies regarding the
%quality of the decompositions they find.  EVALUATION CRITERION
One important test for a software clustering algorithm is to apply it to a
collection of software systems with known reference decompositions made by
experienced developers \cite{Anquetil1999}. It is expected that a good algorithm
finds decompositions that are similar to reference decompositions, which can be
measured by a similarity metric such as MoJo \cite{Tzerpos1999} or EdgeSim
\cite{Mitchell2001}.

@@

An alternative approach is to run the algorithms on synthetic, i.e., computer-
generated, component dependency networks with built-in reference decompositions.
This approach enables one to test algorithms with arbitrarily large samples in a
controlled manner. Nevertheless, this approach is often overlooked, mainly
because naïve random network models synthesize networks that are very dissimilar
from component dependency networks.

@@

The paper is organized as follows: Section \ref{sec:models} presents three
network models.
%
Section \ref{sec:characterization} demonstrates a method to tell if a network
resembles a software network.
%
Section \ref{sec:evaluation} shows empirically that the three models synthesize
networks that resemble software networks.
%
Section \ref{sec:conclusion} discusses the impact of this research and future
work.

@@

Network theory has been applied to class dependency networks, represented as
directed unweighted graphs, and it was shown that they are also scale-free
\cite{Myers2003,Valverde2002}. Thus, the study of the structure of
object-oriented software systems can benefit from the vast literature available
about scale-free networks.

>>>>

Large software systems need to be decomposed in modules in order to be
effectively maintained by groups of developers working concurrently. Software
clustering algorithms
\cite{Mancoridis1998,Anquetil1999,Tzerpos2000,Andritsos2005}, also known as
architecture recovery algorithms, can automatically find a suitable
decomposition by analyzing the dependencies between components in a software
system (e.g., classes in object-oriented systems) and then grouping together
highly interdependent components.

Although many software clustering algorithms have been proposed, there is little
empirical evaluation regarding the external quality of the decompositions they
found. One important test for a software clustering algorithm is to apply it to
a collection of software systems with known reference decompositions made by
experienced developers \cite{Anquetil1999}. It is expected that a good algorithm
finds decompositions that are similar to reference decompositions, which can be
measured by a similarity metric such as MoJo \cite{Tzerpos1999} or EdgeSim
\cite{Mitchell2001}.

@@

An alternative approach is to run the algorithms on synthetic, i.e., computer-
generated, component dependency networks with built-in reference decompositions.
This approach enables one to test algorithms with arbitrarily large samples in a
controlled manner. Nevertheless, this approach is often overlooked, mainly
because networks synthesized by naïve random network models are very dissimilar
from real component dependency networks.

@@

The paper is organized as follows: Section \ref{sec:models} presents three
network models.
%
Section \ref{sec:characterization} demonstrates a method to tell if a network
resembles a software component dependency network.
%
Section \ref{sec:evaluation} shows empirically that the three models synthesize
networks that resemble software component dependency networks.
%
Section \ref{sec:conclusion} discusses the impact of this research and future
work.

@@

Network theory has been applied to class dependency networks, represented as
directed unweighted graphs, and it was shown that they are also scale-free
\cite{Myers2003,Valverde2002}. Thus, the study of the structure of
object-oriented software systems can benefit from the vast literature available
about scale-free networks. In the remaining of this paper, we will use the
expression ``software network'' to refer to a network of static dependencies
between classes of a software system, in contrast to networks studied in other
domains.
